---
title: "What is with News headlines ? - Text, Sentimental Analysis"
author: "Hitesh Palamada"
date: "8 August 2017"
output: html_document
---
Headlines make a huge difference in how readers understand articles,especially if they’re voracious speed-readers.
This headlines want lots of people to read article. 
The point is to get the attention of the reader and draw him into the story.

##The Mind Is Like a Magnet 
Lets see how sentiments behind the Headlines makes us to read them.


```{r, message=FALSE, warning=FALSE}
# Importing Library

library('syuzhet') #for sentiments analysis
library(readr)
library(dplyr)
library(tidyverse)

```

##Import data set
```{r, message=FALSE, warning=FALSE}
abcnews <- read_csv("../input/abcnews-date-text.csv")

```

## Sentiment Analysis

```{r, message=FALSE, warning=FALSE}

#Getting year column from publish_date
abcnews$year<-substr(abcnews$publish_date, start = 1, stop = 4)

head(abcnews)
dim(abcnews)

abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017))

```

```{r, message=FALSE, warning=FALSE}

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))


td_new <- data.frame(rowSums(td[2:69179]))     
# Selecting only 69179 columns as kaggle throws error message with all columns selected


#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[1:10,]

#Vizualisation
library("ggplot2")


qplot(sentiment, data=td_new2, weight=count, geom="bar",fill=sentiment)+ggtitle("Abc News headlines sentiment analysis")

```

```{r, message=FALSE, warning=FALSE, echo = FALSE}


bp<- ggplot(td_new2, aes(x=sentiment, y=count, fill=td_new2$sentiment))+
geom_bar(width = 1, stat = "identity")
bp+ coord_polar("x", start=0) + theme(legend.position="none")+labs( x = "", y = "")+theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

```

###Our brains make sense of the universe by seeing patterns in things. Things that don't fit the pattern are what becomes important.
###conclusion : To grab on attention of readers, most News Headlines have sentiments of Negative and fear.

###From Rohk request of ploting sentiment changes with year, i have created another kernal-" What is with News headlines Part-2" [Click HERE](https://www.kaggle.com/hiteshp/whats-with-news-headlines-part-2/notebook).


```{r include=FALSE}
options(tibble.width = Inf)
```



###Lets see year wise Abc News headlines sentiment analysis{.tabset}

#### 2003 

```{r, result='asis', echo = FALSE}
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == 2003)

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:7000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[1:10,]

qplot(sentiment, data=td_new2, weight=count, geom="bar",fill=sentiment)+ggtitle("Abc News headlines sentiment analysis for 2003")


bp<- ggplot(td_new2, aes(x=sentiment, y=count, fill=td_new2$sentiment))+
geom_bar(width = 1, stat = "identity")
bp+ coord_polar("x", start=0) + theme(legend.position="none")+labs( x = "", y = "")+theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

 
```

#### 2004

```{r, result='asis',  echo = FALSE}
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == 2004)

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:7000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[1:10,]

qplot(sentiment, data=td_new2, weight=count, geom="bar",fill=sentiment)+ggtitle("Abc News headlines sentiment analysis for 2004")


bp<- ggplot(td_new2, aes(x=sentiment, y=count, fill=td_new2$sentiment))+
geom_bar(width = 1, stat = "identity")
bp+ coord_polar("x", start=0) + theme(legend.position="none")+labs( x = "", y = "")+theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))
        
```

#### 2005

```{r, result='asis', echo = FALSE}
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == 2005)

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:7000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[1:10,]


qplot(sentiment, data=td_new2, weight=count, geom="bar",fill=sentiment)+ggtitle("Abc News headlines sentiment analysis for 2005")


bp<- ggplot(td_new2, aes(x=sentiment, y=count, fill=td_new2$sentiment))+
geom_bar(width = 1, stat = "identity")
bp+ coord_polar("x", start=0) + theme(legend.position="none")+labs( x = "", y = "")+theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))
        
 
```





##Lets lookin to Word clould of Abc News Headlines


```{r, message=FALSE, warning=FALSE}
library(tm)
library(wordcloud)
makeWordCloud <- function(documents) {
  corpus = Corpus(VectorSource(tolower(documents)))
  corpus = tm_map(corpus, removePunctuation)
  corpus = tm_map(corpus, removeWords, stopwords("english"))
  
  frequencies = DocumentTermMatrix(corpus)
  word_frequencies = as.data.frame(as.matrix(frequencies))
  
  words <- colnames(word_frequencies)
  freq <- colSums(word_frequencies)
  wordcloud(words, freq,
            min.freq=sort(freq, decreasing=TRUE)[[100]],
            colors=brewer.pal(8, "Dark2"),
            random.color=TRUE) 
}  

makeWordCloud(abcnews[["headline_text"]][1:2000])

```


####Hmmm, Colourfull
####Lets lookin to most frequently words used 

```{r, message=FALSE, warning=FALSE}
library(tidytext)

title_words <- abcnews %>%
   select(publish_date, headline_text) %>%
    unnest_tokens(Word , headline_text)

title_word_counts <- title_words %>%
    anti_join(stop_words, c(Word = "word")) %>%
    count(Word, sort = TRUE)

title_word_counts %>%
    head(20) %>%
    mutate(Word = reorder(Word, n)) %>%
    ggplot(aes(Word, n)) +
    geom_bar(stat = "identity") +
    ylab("Number of appearances in R question titles") +
    coord_flip()


```



#Most of Headlines are about  Police, Court, council, govt, Iraq, war  and water, rain, fire, death.







###That's all for now. Thanks for reading. If you have any feedback, I'd love to hear! I appreciate all the feedback.
###Do visit another intresting kernel “What is with News headlines Part-2” [CLICK HERE](https://www.kaggle.com/hiteshp/whats-with-news-headlines-part-2/notebook)
###Please like the kernel. Your likes are my motivation. :)

