---
title: "What is with News headlines ? - Part-2"
author: "Hitesh Palamada"
date: "8 August 2017"
output: html_document
---
Headlines make a huge difference in how readers understand articles,especially if they’re voracious speed-readers.
This headlines want lots of people to read article. 
The point is to get the attention of the reader and draw him into the story.

##The Mind Is Like a Magnet 

This kernel is continuation of "What is with News headlines" [here](https://www.kaggle.com/hiteshp/what-is-with-news-headlines/notebook). 


Please do look, its intresting!!


```{r, message=FALSE, warning=FALSE}
# Importing Library

library('syuzhet') #for sentiments analysis
library(readr)
library(dplyr)
library(tidyverse)

```

##Import data set
```{r, message=FALSE, warning=FALSE}
abcnews <- read_csv("../input/abcnews-date-text.csv")

```

## Sentiment Analysis

```{r, message=FALSE, warning=FALSE}

#Getting year column from publish_date
abcnews$year<-substr(abcnews$publish_date, start = 1, stop = 4)


```

###Lets see last 10 year wise Abc News headlines sentiment analysis

```{r, message=FALSE, warning=FALSE, echo=FALSE }


#2007
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2007))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2007<-td_new[1:10,]

td2007$year<- 2007

#2008
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2008))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2008<-td_new[1:10,]

td2008$year<- 2008

#2009
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2009))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2009<-td_new[1:10,]

td2009$year<- 2009


#2010
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2010))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2010<-td_new[1:10,]

td2010$year<- 2010

#2011
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2011))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2011<-td_new[1:10,]

td2011$year<- 2011


#2012
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2012))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2012<-td_new[1:10,]

td2012$year<- 2012

#2013
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2013))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2013<-td_new[1:10,]

td2013$year<- 2013

#2014
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2014))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2014<-td_new[1:10,]

td2014$year<- 2014

#2015
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2015))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2015<-td_new[1:10,]

td2015$year<- 2015

#2016
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2016))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2016<-td_new[1:10,]

td2016$year<- 2016

#2017
abcnews1 <- abcnews %>%
select(year, headline_text) %>%
 filter(year == c(2017))

d<-get_nrc_sentiment(abcnews1$headline_text)
td<-data.frame(t(d))

td_new <- data.frame(rowSums(td[2:5000]))     

#Transformation and  cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td2017<-td_new[1:10,]

td2017$year<- 2017

df <- rbind(td2007,td2008,td2009,td2010,td2011,td2012,td2013,td2014,td2015,td2016,td2017)

df %>% 
    ggplot(aes(x=as.integer(year), y=count)) +
    geom_line(color='red', stat='identity') + 
    geom_point(color='red', size=2) + 
    scale_x_continuous(breaks=seq(1,12,1)) + 
    facet_wrap(~  sentiment) +
    labs(x='year', title='change of sentiments with year')


```





###That's all for now. Thanks for reading. If you have any feedback, I'd love to hear! I appreciate all the feedback.
### Do visit another intresting kernal "What is with News headlines" [here](https://www.kaggle.com/hiteshp/what-is-with-news-headlines/notebook) and 
### Please like the kernel, Your likes are my motivation.  :)

